### 2014-10-21 ApTranscriptome_TR.Rmd
added figure to compare log ratio of inducibility to log ratio of baseline expression

png("results/constitutive_vs_inducibility_A22high.png")
gg9
dev.off()
```

>>>>

png("results/constitutive_vs_inducibility_A22high.png")
gg9
dev.off()

Ar.high.transcripts.df <- Ap.response.type[which(Ap.response.type$Ar.type == "High"), ]
Ap.response.type2.Ar.high <- Ap.response.type2[Ap.response.type2$Transcript %in% Ar.high.transcripts.df$Transcript, ]
str(Ap.response.type2.Ar.high)

gg10 <- ggplot(Ap.response.type2.Ar.high, aes(x = log(A22.opt), y = log(Ar.opt), colour = A22.type)) + 
  geom_point() + 
  geom_smooth() +
  labs(x="log(consitutive expression of A. picea)", y = "log(Degree of inducibility in A. carolinensis)")

#+
  #theme(legend.position = "none")

gg10 + geom_abline(intercept=0, slope=1)
```

```{r log_inducibility}
str(Ar.high.transcripts.df)
Ap.response.type2.A22.high <- Ap.response.type2[Ap.response.type2$Transcript %in% Ar.high.transcripts.df$Transcript, ]
str(Ap.response.type2.A22.high)

# exclude transcripts with zero upregulation for denominator
Ap.response.type2.A22.high <- Ap.response.type2.A22.high[which(Ap.response.type2.A22.high$Ar.upreg != 0), ]

Ap.response.type2.A22.high$A22.Ar.upreg <- Ap.response.type2.A22.high$A22.upreg / Ap.response.type2.A22.high$Ar.upreg

# exclude transcripts with zero ratio of upregulation
Ap.response.type2.A22.high <- Ap.response.type2.A22.high[which(Ap.response.type2.A22.high$A22.Ar.upreg != 0), ]

# ratio of baseline expression
Ap.response.type2.A22.high$Ar.A22.baseline <- Ap.response.type2.A22.high$Ar.opt / Ap.response.type2.A22.high$A22.opt

head(Ap.response.type2.A22.high)

# plot!
gg11 <- ggplot(Ap.response.type2.A22.high, aes(y = log(A22.Ar.upreg+0.01), x = log(Ar.A22.baseline))) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(y="log(inducibility A. picea / inducibility A. car)", x = "log(baseline A. carolinensis / baseline A. picea)")

summary(lm(log(A22.Ar.upreg) ~ log(Ar.A22.baseline), data = Ap.response.type2.A22.high))

cor.test(log(Ap.response.type2.A22.high$A22.Ar.upreg), log(Ap.response.type2.A22.high$Ar.A22.baseline))

### Repeat for A. carolinensis *Low* transcripts

str(Ar.low.transcripts.df)
Ap.response.type2.Ar.low <- Ap.response.type2[Ap.response.type2$Transcript %in% Ar.low.transcripts.df$Transcript, ]
str(Ap.response.type2.Ar.low)

# ratio of upregulation
Ap.response.type2.Ar.low$Ar.A22.upreg <- Ap.response.type2.Ar.low$Ar.upreg / Ap.response.type2.Ar.low$A22.upreg

# exclude transcripts with zero ratio of upregulation
Ap.response.type2.Ar.low <- Ap.response.type2.Ar.low[which(Ap.response.type2.Ar.low$Ar.A22.upreg != 0), ]

Ap.response.type2.Ar.low$A22.Ar.baseline <- Ap.response.type2.Ar.low$A22.opt / Ap.response.type2.Ar.low$Ar.opt

head(Ap.response.type2.Ar.low)

gg12 <- ggplot(Ap.response.type2.Ar.low, aes(y = log(Ar.A22.upreg), x = log(A22.Ar.baseline))) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(y="log(inducibility A. car / inducibility A. picea)", x = "log(baseline A. picea / baseline A. car)")

gg12
```
